Preregistration analysis, Cost 2 study

### 2019-05-10 Cost2/Cost2_prereg.Rmd
mostly matched now!

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Reward"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```

>>>>

# Plot coeffs
temp <- melt(logisRH[c("Handling", "Reward"), ])
qplot(data = temp, x = Var1, y = value, geom = "boxplot") + 
  labs(x = "", y = "Coefficients") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme(legend.position = c(0.9, 0.7),
       panel.grid.major = element_blank(), 
       panel.grid.minor = element_blank(), 
       panel.background = element_blank(), 
       axis.line = element_line(colour = "black"),
       text = element_text(size = 16))
```
